Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-09 automatica/paper.tex
todo
remove bit about lines of code

Our CEGIS engine is implemented as an integrated module within the C bounded
model checker (CBMC)~\cite{ClarkeKL04}.  CBMC transforms the ANSI-C representation
of our closed-loop control system model into its internal representation (IR).  We
instrument this IR for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
underlying SAT or SMT solver to solve verification conditions.  We~model FWL
effects, time discretization and the presence of quantization noise
explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
\texttt{CPROVER\_assume} intrinsic functions).  Our module is included into
CBMC~5.7 and is available for
download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
\textcolor{red}{Lucas: I'll need support from Pascal to create this VirtualBoxOVA}
We further created a VirtualBox OVA image with our tool pre-installed,
including our MATLAB-generated benchmarks and benchmark shell script with
instructions to run all benchmarks and reproduce our
experiments.\footnote{\url{XXXXXXXXXX}}

\textcolor{red}{This paragraph needs to be updated by Elizabeth and Dario.}

The entire implementation consists of $XXX$ and $XXX$ lines of C code in the multi-stage and abstract
accelerator back-ends, respectively, $XXXX$ lines of C code for utility functions such as interval, 
fixed- and floating-point arithmetic, as well as $1000$ lines of C++ code in the control synthesis
module in CEGIS CBMC.  We evaluate \tool~using $XXX$ SISO control system
benchmarks.

@@

%-------------------------------
\subsection{Description of the control benchmarks}
\label{exp:benchmarks}
%-------------------------------

The \textit{acrobot} (\#1) plant corresponds to the model of a two-link 
underactuated robot manipulator, 
%named acrobot, 
linearized by partial feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark (\#2) 
describes the dynamics of the azimuth angle of an antenna 
motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. 
The \textit{ballmaglev} (\#3) plant corresponds to the model of a simple 
eletromagnet-ball system, where a steel ball can be levitated by the force generated by an electromagnet~\cite{Franklin15}.  
The \textit{bioreactor} benchmark (\#4) is a linear model 
%identified by least squares 
of the cell mass concentration controlled through the dilution rate of a bioreactor~\cite{bioreactor}.

>>>>

Our CEGIS engine is implemented as an integrated module within the C bounded
model checker (CBMC)~\cite{ClarkeKL04}.  CBMC transforms the ANSI-C representation
of our closed-loop control system model into its internal representation (IR).  We
instrument this IR for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
underlying SAT or SMT solver to solve verification conditions.  We~model FWL
effects, time discretization and the presence of quantization noise
explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
\texttt{CPROVER\_assume} intrinsic functions).  Our module is included into
CBMC~5.7 and is available for
download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
We further created a VirtualBox OVA image with our tool pre-installed,
including our MATLAB-generated benchmarks and benchmark shell script with
instructions to run all benchmarks and reproduce our
experiments.\footnote{\note{\url{XXXXXXXXXX}}}
%
%\textcolor{red}{This paragraph needs to be updated by Elizabeth and Dario.}
%
%The entire implementation consists of $XXX$ and $XXX$ lines of C code in the multi-stage and abstract
%accelerator back-ends, respectively, $XXXX$ lines of C code for utility functions such as interval, 
%fixed- and floating-point arithmetic, as well as $1000$ lines of C++ code in the control synthesis
%module in CEGIS CBMC.  We evaluate \tool~using $XXX$ SISO control system
%benchmarks.

@@

%-------------------------------
\subsection{Description of the control benchmarks}
\label{exp:benchmarks}
%-------------------------------
\note{redo number and remove benchmarks that we can't solve}
The \textit{acrobot} (\#1) plant corresponds to the model of a two-link 
underactuated robot manipulator, 
%named acrobot, 
linearized by partial feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark (\#2) 
describes the dynamics of the azimuth angle of an antenna 
motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. 
The \textit{ballmaglev} (\#3) plant corresponds to the model of a simple 
eletromagnet-ball system, where a steel ball can be levitated by the force generated by an electromagnet~\cite{Franklin15}.  
The \textit{bioreactor} benchmark (\#4) is a linear model 
%identified by least squares 
of the cell mass concentration controlled through the dilution rate of a bioreactor~\cite{bioreactor}.
